Journey: A Study of Studying Large Memory Systems

### 2017-04-12 paper.tex
A bit of clean up

In this experiment, a single process touches 32GB of virtual memory, leading to
the actual allocation of physical memory. Notice that 32GB is twice as large as
the 16GB of physical memory the test machine. This causes Linux kernel to start
swapping out pages to make more room.  After each page of virtual memory is
touched, the resident set size (RSS; the amount of physical memory Linux has
allocated to the process) is recorded. This value is graphed in our results
section.

This experiment with 5 different swapfile sizes to capture the impact
of swapfile size on swapping overhead.

@@

During this experiment, the values of RSS are stored in a mlocked array and
written to a file after the benchmark completes. This prevents the writing of
the results from interacting with paging.

>>>>

In this experiment, a single process touches 32GB of virtual memory, leading to
the actual allocation of physical memory. Notice that 32GB is twice as large as
the 16GB of physical memory in the test machine, causing Linux to start paging
after physical memory is exhausted. Also, notice that the Linux kernel will
reserve some memory for its own operation.

After each page of virtual memory is touched, the resident set size (RSS; the
amount of physical memory Linux has allocated to the process) is recorded.  The
values of RSS are stored in an mlocked array and written to a file after the
benchmark completes. This prevents the writing of the results from interacting
with paging.  These RSS values are graphed in our results section.

This experiment is repeated with 5 different swapfile sizes to capture the
impact of swapfile size on swapping overhead.

@@
